\SuperScreen: An open-source package for simulating the magnetic response of two-dimensional superconducting devices

### 2022-06-06 response-to-reviewer-comments.tex

\usepackage{geometry} % This package allows the editing of the page layout
\usepackage{amsmath}  % This package allows the use of a large range of mathematical formula, commands, and symbols
\usepackage{ulem,xcolor}

\title{Response to reviewer comments}
\author{Logan Bishop-Van Horn}
\date{\today}

\begin{document}
\maketitle

In the revised manuscript, text that should be removed is shown in \textcolor{red}{red} with a strikethough, \textcolor{red}{\sout{like this}}, and text that has been modified or added is shown in \textcolor{blue}{blue, like this}.

@@

\begin{itemize}
    \item{
    {\bf Reviewer comment:} ``The manuscript is well written and the work is of interest to the applied superconductivity community.''

    {\bf Author response:} We are glad that the reviewer found the paper to be well written, and we agree that the software and manuscript will be valuable to the applied superconductivity community.
    }
    \item{
    {\bf Reviewer comment:} ``The software works, although the implementation is a bit slower and more memory hungry than commercial or closed-source tools.''

    {\bf Author response:} It is true that the software favors portability and simplicity of implementation over raw performance, likely making it less efficient than some commercial or closed-source tools. We do not see SuperScreen as a competitor to or replacement for superconducting electronic design automation (EDA) and inductance extraction tools such as InductEx and FastHenry. Rather, we see SuperScreen as a complementary research tool for modeling experiments involving 2D superconductors and mesoscopic superconducting devices, as opposed to designing superconducting integrated circuits. 
    }
    \item{
    {\bf Reviewer comment:} ``The reference to [16] for a review of inductance extraction is a bit old -- newer tools and methods and publications exist.''

    {\bf Author response:} Reference [16] (Gaj, \textit{et al.}) is indeed a bit old. We have added more recent references about inductance extraction tools to Appendix A. In particular, Tolpygo, \textit{et al.} 2021 Supercond. Sci. Technol. {\bf 34} 085005 (which is now cited as reference [20]) and references [8--25] therein provide a thorough and up-to-date survey of inductance extraction software.
    }
    \item{
    {\bf Reviewer comment:} ``P.4, Left Column, Line 53: `though' should be `through'.''

### 2022-06-06 highlights.tex
Updates from Overleaf

\begin{document}
\maketitle
\begin{itemize}
    \item{SuperScreen is an open-source Python package that solves the London equation to simulate the Meissner response of two-dimensional superconductors for any value of the effective magnetic penetration depth.}
    \item{The package provides an intuitive object-oriented interface for the creation of models with complex geometries, and for post-processing and visualization of simulation results.}
    \item{The package can be used to calculate self- and mutual inductance in thin film superconducting devices.}
    \item{SuperScreen can be used to model flux trapping and fluxoid quantization effects and calculate the supercurrent distribution due to Pearl vortices in two-dimensional superconductors.}
    \item{SuperScreen enables quantitative modeling of the supercurrent distribution in mesoscopic superconducting devices to help inform and interpret measurements.}
\end{itemize}
\end{document}

>>>>

\begin{document}
\maketitle
\begin{itemize}
    \item{SuperScreen is an open-source Python package that solves the London equation to simulate the Meissner response of two-dimensional superconductors for any value of the effective magnetic penetration depth.}
    \item{The package provides an intuitive object-oriented interface for the creation of models with complex geometries, and for post-processing and visualization of simulation results.}
    \item{The package can be used to calculate self- and mutual inductance in thin film superconducting devices.}
    \item{SuperScreen can be used to model flux trapping and fluxoid quantization effects, and calculate the supercurrent distribution due to Pearl vortices in two-dimensional superconductors.}
    \item{SuperScreen enables quantitative modeling of the supercurrent distribution in mesoscopic superconducting devices to help inform and interpret measurements.}
\end{itemize}
\end{document}

### 2022-06-06 main.tex
Updates from Overleaf

@@

\begin{abstract}
Quantitative understanding of the spatial distribution of magnetic fields and Meissner screening currents in two-dimensional (2D) superconductors and mesoscopic thin film superconducting devices is critical to interpreting the results of magnetic measurements of such systems. Here, we introduce \SuperScreen, an open-source Python package for simulating the response of 2D superconductors to trapped flux and applied time-independent or quasi-DC magnetic fields for any value of the effective magnetic penetration depth, $\Lambda$. Given an applied magnetic field, \SuperScreen solves the 2D London equation using an efficient matrix inversion method~\cite{Brandt2004-ew, Brandt2005-wj} to obtain the Meissner currents and magnetic fields in and around structures composed of one or more superconducting thin films of arbitrary geometry. \SuperScreen can be used to model screening effects and calculate self- and mutual-inductance in thin film superconducting devices.
\end{abstract}

@@

\SuperScreen is a Python package developed to simulate the static magnetic response of structures composed of one or more layers containing superconducting thin films characterized by a London penetration depth $\lambda$ that is large compared to the film thickness $d$. \SuperScreen solves the coupled Maxwell's and London's equations in and around superconducting films in the presence of inhomogeneous applied magnetic fields, pinned vortices, and trapped flux using a matrix inversion method introduced by Brandt and Clem~\cite{Brandt2004-ew,Brandt2005-wj} and subsequently used by Kirtley, \emph{et al.} to model the magnetic response of scanning superconducting quantum interference device (SQUID) sensors~\cite{Kirtley2016-zz, Kirtley2016-gt}.

There have been many previous numerical studies of magnetic screening and inductance extraction in thin film and two-dimensional (2D) superconducting devices~\cite{Jaycox1981-zl, Ketchen1982-at, Ketchen2012-mb, Hildebrandt1995-uw, Khapaev1997-kw, Khapaev2001-xq, Khapaev2001-pw, Khapaev2002-ev,  Babaei_Brojeny2003-la, Brandt2004-ew, Brandt2005-wj, Clem2005-ye, Muller2021-ci, Fourie2011-wl, Fourie2012-gv, Jackman2016-mf}. However, few software tools for this task exist and those that are available are closed-source, are written in low-level compiled languages like C, and/or require the use of specialized file formats or separate computer aided design (CAD) software for defining device geometries and model configurations.\footnote{A brief summary of existing tools can be found in \ref{appendix:other-tools}, and a more thorough overview in Ref.~\cite{Gaj1999-ls}.} Most of these tools are intended for use in the design of superconducting integrated circuits for single flux quantum (SFQ) logic and are primarily used for inductance extraction~\cite{Gaj1999-ls, Tolpygo2021-jz}. \SuperScreen is an open-source, user-friendly, portable research tool designed to lower the barrier to entry to quantitative modeling of 2D superconductors, and to help interpret and inform measurements of superconducting thin films and devices.

@@

A convenient method for solving this problem was introduced by Brandt and Clem in Ref.~\cite{Brandt2004-ew}, expanded by Brandt in Ref.~\cite{Brandt2005-wj}, and subsequently used to model the magnetic response of scanning SQUID susceptometers~\cite{Kirtley2016-zz, Kirtley2016-gt}. In the London model of superconductivity, the magnetic field $\vec{H}(\vec{r})$ and 3D current density $\vec{j}(\vec{r})$ in a superconductor with London penetration depth $\lambda$ obey the second London equation:
$\vec{H}(\vec{r})-\lambda^2\vec{\nabla}\times\vec{j}(\vec{r})=$, where
$\vec{\nabla}=\left(\frac{\partial}{\partial x}, \frac{\partial}{\partial y}, \frac{\partial}{\partial z}\right)$ is the 3D gradient operator. The 2D London model assumes that the current density $\vec{j}$ is approximately independent of $z$, such that  $\vec{j}(\vec{r}) = \vec{j}(x, y, z)\approx\vec{j}_{z_0}(x, y)$ for a film lying parallel to the $x-y$ plane at vertical position $z_0$. Working now with the thickness-integrated current density $\vec{J}(x, y)=\vec{j}_{z_0}(x, y)\cdot d$, where $d$
is the thickness of the film, the second London equation reduces to
\begin{equation}
    \label{eq:london}
    \vec{H}(x, y)=-\Lambda\vec{\nabla}\times\vec{J}(x, y)\\
\end{equation}
where $\Lambda=\lambda^2/d$ is the effective penetration depth
of the superconducting film (equal to half the Pearl length~\cite{Pearl1964-cl}) and $\vec{\nabla}=\left(\frac{\partial}{\partial x}, \frac{\partial}{\partial y}\right)$ is now the 2D gradient operator.

It is important to note that the assumption $\vec{j}(x, y, z)\approx\vec{j}_{z_0}(x, y)$ is valid for only films that are thinner than their London penetration depth ($d\ll\lambda$, such that $\Lambda=\lambda^2/d\gg\lambda$). However the model has been applied with some success in structures with $\lambda\lesssim d$, for example by Kirtley, \emph{et al.} in modeling the magnetic response of scanning SQUID susceptometers~\cite{Kirtley2016-zz,Kirtley2016-gt}. Aside from this limitation, the method described below can be used to model films with any effective penetration depth $0\leq\Lambda<\infty$.

@@

The matrix version of Eq.~\ref{eq:Heff_sub} is
\begin{equation}
    \label{eq:Heff_sub_num}
     \mathbf{h}_{z,\,\mathrm{applied}} - \sum_{\mathrm{holes}\, h}\mathbf{h}_{z,\,\mathrm{eff},\,h} = -(\mathbf{Q}.\mathbf{w}^T-\Lambda\mathbf{\nabla}^2)\mathbf{g},
\end{equation}
where we exclude points in the mesh lying outside of the superconducting film but keep points
inside holes in the film. $\mathbf{\nabla}^2$
is the Laplace operator, a $p\times p$ matrix defined such that $\mathbf{\nabla}^2\mathbf{f}$ computes the Laplacian $\nabla^2f(x,y)$ of a scalar field $f(x,y)$ defined on the mesh vertices (see~\ref{appendix:laplace}).

@@

\SuperScreen allows one to calculate the fluxoid $\Phi^f_S$ for any polygonal region $S$ whose boundary $\partial S$ lies completely within a superconducting film using the method \inline{Solution.polygon_fluxoid()} (see Section~\ref{section:model:fluxoid}, Eq.~\ref{eq:fluxoid}). The ``flux part''  $\int_S\mu_0H_z(\vec{r})\,\mathrm{d}^2r$ is calculated using \inline{Solution.polygon_flux()}, which computes the flux through a polygon representing a region $S$ as $\Phi_S=\sum_{i\in S} \mu_0H_{z,i}w_i$, where $H_{z,i}$ is the magnetic field at vertex $i$ (recall that $w_i$ assigns an effective area to mesh vertex $i$). The ``supercurrent part'' $\oint_S\mu_0\Lambda\vec{J}(\vec{r})\cdot\mathrm{d}\vec{r}$ is calculated by evaluating the vector current density $\vec{J}$ at each point in the path $\partial S$ using \inline{Solution.interp_current_density()}, then computing the line integral along the path using the trapezoid rule. The sum of these two terms gives the fluxoid $\Phi^f_S$.

@@

The ability to model and visualize screening effects in 2D superconductors and devices constructed from superconducting thin films can help to build intuition about these systems, aid in interpretation of measurement results, and enable optimization of measurement and device design. \SuperScreen is an open-source, user-friendly, portable, and efficient tool that solves this problem. Applications of the package include calculating self- and mutual-inductance in planar and multi-planar superconducting circuits, and modeling the magnetic interaction between superconducting samples and superconducting sensors such as scanning SQUID susceptometers~\cite{Kirtley2016-zz}.

@@

Here, we briefly describe existing software tools for modeling the magnetic response of superconducting devices, most of which are specifically designed for inductance extraction for superconducting integrated circuits. FastHenry, a widely-used 3D (normal metal) inductance extraction tool from MIT~\cite{Kamon1994-ck}, has been extended to support superconducting elements~\cite{wrcad, XicTools}. This modified version of FastHenry has been used for inductance extraction in the commercial software InductEx~\cite{Fourie2011-wl, Fourie2012-gv, Jackman2016-mf}. While FastHenry is open-source, it is written in C and must be compiled for a specific computer architecture and operating system. FastHenry executables compiled for several common operating systems are available as part of the open-source XicTools superconducting integrated circuit design suite from Whiteley Research, Inc~\cite{wrcad, XicTools}. A 2D London-Maxwell approach based on a scalar stream function, much like the approach used by \SuperScreen~\cite{Brandt2004-ew, Brandt2005-wj}, forms the basis of the 3D-MLSI software package~\cite{Khapaev1997-kw, Khapaev2001-xq, Khapaev2001-pw, Khapaev2002-ev}, which is also written in C and is not open-source. For a thorough historical overview and comparison of inductance extraction tools, see Ref.~\cite{Gaj1999-ls}. For a more recent overview of superconducting inductance extraction tools see Ref.~\cite{Tolpygo2021-jz}, particularly references [8--25] therein.

\SuperScreen is not intended primarily as an inductance extraction tool and cannot be used to extract the inductance of superconducting transmission lines (a common superconducting circuit design task~\cite{Gaj1999-ls,Khapaev1996-uu,Tolpygo2021-jz}) due to the lack of support for ``terminal currents.'' Nevertheless, it is instructive to compare \SuperScreen to a state of the art commercial inductance extraction tool, InductEx~\cite{Fourie2011-wl, Fourie2012-gv, Jackman2016-mf}, on a problem that can be solved using both tools. One such problem, provided as an example in the InductEx user manual, is the self-inductance $L$ of a square washer with outer dimension $30\,\um$, inner dimension $10\,\um$, London penetration depth $\lambda=0.24\,\um$, and film thickness $d=0.20\,\um$, for which the InductEx solution reports a ``design'' value of $L=20\,\mathrm{pH}$ and an ``extracted'' value of $L=20.0956\,\mathrm{pH}$~\cite{inductex_user_manual_2020}. Code Block~\ref{code:washer} demonstrates how to solve this problem using \SuperScreen. The inductance extracted using \SuperScreen, $L=19.91\,\mathrm{pH}$, is within 1\% of the inductance extracted using InductEx.

@@

layer = sc.Layer(
    "base",
    london_lambda=0.24,
    thickness=0.2,
)
film = sc.Polygon(
    "washer",
    layer="base",
    points=box(30, points_per_side=50),
)
hole = sc.Polygon(
    "hole",
    layer="base",
    points=box(10, points_per_side=250),
)
device = sc.Device(
    "washer",
    layers=[layer],
    films=[film],
    holes=[hole],
    length_units="um",
)
device.make_mesh(min_points=3000)
# See Equation 19.
M = device.mutual_inductance_matrix()
L = M[0, 0].to("pH")
print(f"Inductance = {L:~.4fP}")
# Output: Inductance = 19.9100 pH
\end{minted}
\captionof{listing}{\SuperScreen script to calculate the self-inductance of a square washer with outer dimension $30\,\um$, inner dimension $10\,\um$, London penetration depth $\lambda=0.24\,\um$, and film thickness $d=0.20\,\um$. The extracted inductance $L=19.91\,\mathrm{pH}$ differs from the InductEx ``design'' and ``extracted'' values by -0.45\% and -0.92\% respectively~\cite{inductex_user_manual_2020}. }
\label{code:washer}
\end{code-onecol}

@@

The definitions of the Laplace operator $\mathbf{\nabla}^2$ (also called the Laplace-Beltrami operator) and the gradient operator $\vec{\nabla}=(\nabla_x, \nabla_y)^T$ deserve special attention, as these two operators reduce the problem of solving a partial differential equation to the problem of solving a matrix equation~\cite{Reuter2009-hr}.  Given a mesh consisting of $p$ vertices and $t$ triangles, and a scalar field $f(x, y)$ represented by a $p\times 1$ vector $\mathbf{f}$ containing the values of the field at the mesh vertices, the goal is to construct matrices $\nabla^2$ and $\vec{\nabla}=(\nabla_x, \nabla_y)^T$ such that the matrix products $\nabla^2\mathbf{f}$ and $\vec{\nabla}\mathbf{f}$ approximate the Laplacian $\left(\frac{\partial^2f}{\partial x^2}+\frac{\partial^2f}{\partial y^2}\right)$ and the gradient $\left(\frac{\partial f}{\partial x}, \frac{\partial f}{\partial y}\right)$  of $f(x, y)$ at the mesh vertices.

@@

We construct the two $p\times p$ gradient matrices $\nabla_x$ and $\nabla_y$, using the ``average gradient on a star" (or AGS) approach~\cite{Mancinelli2019-ci}. Briefly, we first construct two $t\times p$ matrices, $\vec{\nabla}_t=(\nabla_{t,x}, \nabla_{t,y})^T$ using ``per-cell linear estimation'' (or PCE)~\cite{Mancinelli2019-ci}, where $\nabla_{t,x}\mathbf{f}$ maps the field values at the vertices $\mathbf{f}$ to an estimate of the $x$-component of the gradient at the triangle centroids (centers-of-mass). The matrices $\nabla_x$ and $\nabla_y$ are then computed by, for each vertex $i$, taking the weighted average of $\nabla_{t,x}$ and $\nabla_{t,y}$ over adjacent triangles $t\in\mathcal{N}(i)$, with weights given by the angle between the two sides of the triangle adjacent to the vertex. The resulting $\vec{\nabla}=(\nabla_x, \nabla_y)^T$ is a $2\times p\times p$ stack of matrices defined such that $\vec{\nabla}\mathbf{f}$ produces a $2\times p$ matrix representing the gradient of $f(x, y)$ at the mesh vertices, with the first and second rows of $\vec{\nabla}\mathbf{f}$ containing the $x$ and $y$ components of the gradient, respectively.

\section{Spatially inhomogeneous $\lambda$}
\label{appendix:inhomogeneous}

The London equation (Equation~\ref{eq:london}) is valid only under the assumption that the London penetration depth $\lambda$, a proxy for the superfluid density, is constant as a function of position~\cite{Tinkham2004-zn}. In cases where the superfluid density varies as a function of position, Ginzburg-Landau theory provides a more accurate description of the magnetic response of the system. Nevertheless, in an effort to model inhomogeneous superconductors using London theory, one can write out the ``inhomogeneous second London equation'' for a superconductor with spatially-varying London penetration depth $\lambda(\vec{r})$~\cite{Cave1986-js, Kogan2011-zn}:
\begin{align}
\begin{split}
    \label{eq:london_inhomogeneous_3d}
    \vec{H}(\vec{r})&=-\vec{\nabla}\times\left(\lambda^2(\vec{r})\vec{j}(\vec{r})\right)\\
    &=-\left(\lambda^2(\vec{r})\vec{\nabla}\times\vec{j}(\vec{r}) + \vec{\nabla}\lambda^2(\vec{r})\times\vec{j}(\vec{r})\right).
\end{split}
\end{align}

@@

Note that, unlike Equation~\ref{eq:london} in which $\Lambda$ is assumed to be constant as a function of position $\pvec{r}$, solutions to Equation~\ref{eq:london_inhomogeneous_2d} do not necessarily satisfy the fluxoid quantization condition $\Phi^f_S=0$ for simply-connected superconducting regions $S$ in which $\vec{\nabla}\Lambda(\pvec{r})\neq0$ , where
\begin{equation}
	\Phi^f_S=\underbrace{\int_S\mu_0H_z(\pvec{r})\,\mathrm{d}^2r}_{\text{``flux part''}} + \underbrace{\oint_S\mu_0\Lambda(\pvec{r})\vec{J}(\pvec{r})\cdot\mathrm{d}\pvec{r}}_{\text{``supercurrent part''}}.
\end{equation}

>>>>

\usepackage{ulem,xcolor}

@@

\begin{abstract}
Quantitative understanding of the spatial distribution of magnetic fields and Meissner screening currents in two-dimensional (2D) superconductors and mesoscopic thin film superconducting devices is critical to interpreting the results of magnetic measurements of such systems. Here, we introduce \SuperScreen, an open-source Python package for simulating the response of 2D superconductors to trapped flux and applied time-independent or quasi-DC magnetic fields for any value of the effective magnetic penetration depth, $\Lambda$. Given an applied magnetic field, \SuperScreen solves the 2D London equation using an efficient matrix inversion method~\cite{Brandt2004-ew, Brandt2005-wj} to obtain the Meissner currents and magnetic fields in and around structures composed of one or more superconducting thin films of arbitrary geometry \textcolor{red}{\sout{with spatially nonuniform magnetic penetration depth}}. \SuperScreen can be used to model screening effects and calculate self- and mutual-inductance in thin film superconducting devices\textcolor{red}{\sout{, and simulate the magnetic response of inhomogeneous 2D superconductors}}.
\end{abstract}

@@

\SuperScreen is a Python package developed to simulate the static magnetic response of structures composed of one or more layers containing superconducting thin films characterized by a London penetration depth $\lambda$ that is large compared to the film thickness $d$. \SuperScreen solves the coupled Maxwell's and London's equations in and around superconducting films in the presence of inhomogeneous applied magnetic fields, pinned vortices, and trapped flux using a matrix inversion method introduced by Brandt and Clem~\cite{Brandt2004-ew,Brandt2005-wj} and subsequently used by Kirtley, \textit{et al.} to model the magnetic response of scanning superconducting quantum interference device (SQUID) sensors~\cite{Kirtley2016-zz, Kirtley2016-gt}.

There have been many previous numerical studies of magnetic screening and inductance extraction in thin film and two-dimensional (2D) superconducting devices~\cite{Jaycox1981-zl, Ketchen1982-at, Ketchen2012-mb, Hildebrandt1995-uw, Khapaev1997-kw, Khapaev2001-xq, Khapaev2001-pw, Khapaev2002-ev,  Babaei_Brojeny2003-la, Brandt2004-ew, Brandt2005-wj, Clem2005-ye, Muller2021-ci, Fourie2011-wl, Fourie2012-gv, Jackman2016-mf}. However, few software tools for this task exist and those that are available are closed-source, are written in low-level compiled languages like C, and/or require the use of specialized file formats or separate computer aided design (CAD) software for defining device geometries and model configurations.\footnote{A brief summary of existing tools can be found in \ref{appendix:other-tools}\textcolor{red}{\sout{, and a more thorough overview in Ref.~\cite{Gaj1999-ls}}}.} Most of these tools are intended for use in the design of superconducting integrated circuits for single flux quantum (SFQ) logic and are primarily used for inductance extraction~\cite{Gaj1999-ls, Tolpygo2021-jz}. \SuperScreen is an open-source, user-friendly, portable research tool designed to lower the barrier to entry to quantitative modeling of 2D superconductors, and to help interpret and inform measurements of superconducting thin films and devices.

@@

A convenient method for solving this problem was introduced by Brandt and Clem in Ref.~\cite{Brandt2004-ew}, expanded by Brandt in Ref.~\cite{Brandt2005-wj}, and subsequently used to model the magnetic response of scanning SQUID susceptometers~\cite{Kirtley2016-zz, Kirtley2016-gt}. In the London model of superconductivity, the magnetic field $\vec{H}(\vec{r})$ and 3D current density $\vec{j}(\vec{r})$ in a superconductor with London penetration depth \textcolor{blue}{$\lambda$ obey the second London equation:
$\vec{H}(\vec{r})/\lambda^2=-\vec{\nabla}\times\vec{j}(\vec{r})$}, where
$\vec{\nabla}=\left(\frac{\partial}{\partial x}, \frac{\partial}{\partial y}, \frac{\partial}{\partial z}\right)$ is the 3D gradient operator. The 2D London model assumes that the current density $\vec{j}$ is approximately independent of $z$, such that  $\vec{j}(\vec{r}) = \vec{j}(x, y, z)\approx\vec{j}_{z_0}(x, y)$ for a film lying parallel to the $x-y$ plane at vertical position $z_0$. Working now with the thickness-integrated current density $\vec{J}(x, y)=\vec{j}_{z_0}(x, y)\cdot d$, where $d$
is the thickness of the film, the second London equation reduces to
\begin{color}{blue}
\begin{equation}
    \label{eq:london}
    \vec{H}(x, y)=-\Lambda\vec{\nabla}\times\vec{J}(x, y)\\
\end{equation}
\end{color}
where \textcolor{blue}{$\Lambda=\lambda^2/d$} is the effective penetration depth
of the superconducting film (equal to half the Pearl length~\cite{Pearl1964-cl}) and $\vec{\nabla}=\left(\frac{\partial}{\partial x}, \frac{\partial}{\partial y}\right)$ is now the 2D gradient operator.

It is important to note that the assumption $\vec{j}(x, y, z)\approx\vec{j}_{z_0}(x, y)$ is valid for only films that are thinner than their London penetration depth ($d\ll\lambda$, such that $\Lambda=\lambda^2/d\gg\lambda$). However the model has been applied with some success in structures with $\lambda\lesssim d$, for example by Kirtley, \textit{et al.} in modeling the magnetic response of scanning SQUID susceptometers~\cite{Kirtley2016-zz,Kirtley2016-gt}. Aside from this limitation, the method described below can be used to model films with any effective penetration depth $0\leq\Lambda<\infty$.

@@

The matrix version of Eq.~\ref{eq:Heff_sub} is
\begin{equation}
    \label{eq:Heff_sub_num}
     \mathbf{h}_{z,\,\mathrm{applied}} - \sum_{\mathrm{holes}\, h}\mathbf{h}_{z,\,\mathrm{eff},\,h} = -(\mathbf{Q}.\mathbf{w}^T-\Lambda\mathbf{\nabla}^2)\mathbf{g},
\end{equation}
where we exclude points in the mesh lying outside of the superconducting film but keep points
inside holes in the film. \textcolor{red}{\sout{$\mathbf{\Lambda}$ is either a scalar or a vector defining the
effective penetration depth at every included vertex in the mesh, and }}$\mathbf{\nabla}^2$
is the Laplace operator, a $p\times p$ matrix defined such that $\mathbf{\nabla}^2\mathbf{f}$ computes the Laplacian $\nabla^2f(x,y)$ of a scalar field $f(x,y)$ defined on the mesh vertices (see~\ref{appendix:laplace}).

@@

\SuperScreen allows one to calculate the fluxoid $\Phi^f_S$ for any polygonal region $S$ whose boundary $\partial S$ lies completely within a superconducting film using the method \inline{Solution.polygon_fluxoid()} (see Section~\ref{section:model:fluxoid}, Eq.~\ref{eq:fluxoid}). The ``flux part''  $\int_S\mu_0H_z(\vec{r})\,\mathrm{d}^2r$ is calculated using \inline{Solution.polygon_flux()}, which computes the flux through a polygon representing a region $S$ as $\Phi_S=\sum_{i\in S} \mu_0H_{z,i}w_i$, where $H_{z,i}$ is the magnetic field at vertex $i$ (recall that $w_i$ assigns an effective area to mesh vertex $i$). The ``supercurrent part'' \textcolor{blue}{$\oint_S\mu_0\Lambda\vec{J}(\vec{r})\cdot\mathrm{d}\vec{r}$} is calculated by evaluating the vector current density $\vec{J}$ at each point in the path $\partial S$ using \inline{Solution.interp_current_density()}, then computing the line integral along the path using the trapezoid rule. The sum of these two terms gives the fluxoid $\Phi^f_S$.

@@

The ability to model and visualize screening effects in \textcolor{red}{\sout{inhomogeneous} }2D superconductors and devices constructed from superconducting thin films can help to build intuition about these systems, aid in interpretation of measurement results, and enable optimization of measurement and device design. \SuperScreen is an open-source, user-friendly, portable, and efficient tool that solves this problem. Applications of the package include calculating self- and mutual-inductance in planar and multi-planar superconducting circuits, and modeling the magnetic interaction between \textcolor{red}{\sout{inhomogeneous} }superconducting samples and superconducting sensors such as scanning SQUID susceptometers~\cite{Kirtley2016-zz}.

@@

Here, we briefly describe existing software tools for modeling the magnetic response of superconducting devices, most of which are specifically designed for inductance extraction for superconducting integrated circuits. FastHenry, a widely-used 3D (normal metal) inductance extraction tool from MIT~\cite{Kamon1994-ck}, has been extended to support superconducting elements~\cite{wrcad, XicTools}. This modified version of FastHenry has been used for inductance extraction in the commercial software InductEx~\cite{Fourie2011-wl, Fourie2012-gv, Jackman2016-mf}. While FastHenry is open-source, it is written in C and must be compiled for a specific computer architecture and operating system. FastHenry executables compiled for several common operating systems are available as part of the open-source XicTools superconducting integrated circuit design suite from Whiteley Research, Inc~\cite{wrcad, XicTools}. A 2D \textcolor{blue}{London-Maxwell approach based on a scalar stream function, much like the approach} used by \SuperScreen~\cite{Brandt2004-ew, Brandt2005-wj}, forms the basis of the 3D-MLSI software package~\cite{Khapaev1997-kw, Khapaev2001-xq, Khapaev2001-pw, Khapaev2002-ev}, which is also written in C and is not open-source. For a thorough historical overview and comparison of inductance extraction tools, see Ref.~\cite{Gaj1999-ls}. \textcolor{blue}{For a more recent overview of superconducting inductance extraction tools see Ref.~\cite{Tolpygo2021-jz}, particularly references [8--25] therein.}

\textcolor{blue}{\SuperScreen is not intended primarily as an inductance extraction tool and cannot be used to extract the inductance of superconducting transmission lines (a common superconducting circuit design task~\cite{Gaj1999-ls,Khapaev1996-uu,Tolpygo2021-jz}) due to the lack of support for ``terminal currents.'' Nevertheless, it is instructive to compare \SuperScreen to a state of the art commercial inductance extraction tool, InductEx~\cite{Fourie2011-wl, Fourie2012-gv, Jackman2016-mf}, on a problem that can be solved using both tools. One such problem, provided as an example in the InductEx user manual, is the self-inductance $L$ of a square washer with outer dimension $30\,\um$, inner dimension $10\,\um$, London penetration depth $\lambda=0.24\,\um$, and film thickness $d=0.20\,\um$, for which the InductEx solution reports a ``design'' value of $L=20\,\mathrm{pH}$ and an ``extracted'' value of $L=20.0956\,\mathrm{pH}$~\cite{inductex_user_manual_2020}. Code Block~\ref{code:washer} demonstrates how to solve this problem using \SuperScreen. The inductance extracted using \SuperScreen, $L=19.91\,\mathrm{pH}$, is within 1\% of the inductance extracted using InductEx.}

@@

layer = sc.Layer(
    "base",
    london_lambda=0.24,
    thickness=0.2,
)
film = sc.Polygon(
    "washer",
    layer="base",
    points=box(30, points_per_side=50),
)
hole = sc.Polygon(
    "hole",
    layer="base",
    points=box(10, points_per_side=250),
)
device = sc.Device(
    "washer",
    layers=[layer],
    films=[film],
    holes=[hole],
    length_units="um",
)
device.make_mesh(min_points=3000)
# See Equation 19.
M = device.mutual_inductance_matrix()
L = M[0, 0].to("pH")
print(f"Inductance = {L:~.4fP}")
# Output: Inductance = 19.9100 pH
\end{minted}
\captionof{listing}{\textcolor{blue}{\SuperScreen script to calculate the self-inductance of a square washer with outer dimension $30\,\um$, inner dimension $10\,\um$, London penetration depth $\lambda=0.24\,\um$, and film thickness $d=0.20\,\um$. The extracted inductance $L=19.91\,\mathrm{pH}$ differs from the InductEx ``design'' and ``extracted'' values by -0.45\% and -0.92\% respectively~\cite{inductex_user_manual_2020}.}}
\label{code:washer}
\end{code-onecol}

@@

\textcolor{blue}{The definitions of the Laplace operator $\mathbf{\nabla}^2$ (also called the Laplace-Beltrami operator) and the gradient operator $\vec{\nabla}=(\nabla_x, \nabla_y)^T$ deserve special attention, as these two operators reduce the problem of solving a partial differential equation to the problem of solving a matrix equation~\cite{Reuter2009-hr}.  Given a mesh consisting of $p$ vertices and $t$ triangles, and a scalar field $f(x, y)$ represented by a $p\times 1$ vector $\mathbf{f}$ containing the values of the field at the mesh vertices, the goal is to construct matrices $\nabla^2$ and $\vec{\nabla}=(\nabla_x, \nabla_y)^T$ such that the matrix products $\nabla^2\mathbf{f}$ and $\vec{\nabla}\mathbf{f}$ approximate the Laplacian $\left(\frac{\partial^2f}{\partial x^2}+\frac{\partial^2f}{\partial y^2}\right)$ and the gradient $\left(\frac{\partial f}{\partial x}, \frac{\partial f}{\partial y}\right)$  of $f(x, y)$ at the mesh vertices.}

@@

\textcolor{blue}{We construct the two $p\times p$ gradient matrices $\nabla_x$ and $\nabla_y$, using the ``average gradient on a star" (or AGS) approach~\cite{Mancinelli2019-ci}. Briefly, we first construct two $t\times p$ matrices, $\vec{\nabla}_t=(\nabla_{t,x}, \nabla_{t,y})^T$ using ``per-cell linear estimation'' (or PCE)~\cite{Mancinelli2019-ci}, where $\nabla_{t,x}\mathbf{f}$ maps the field values at the vertices $\mathbf{f}$ to an estimate of the $x$-component of the gradient at the triangle centroids (centers-of-mass). The matrices $\nabla_x$ and $\nabla_y$ are then computed by, for each vertex $i$, taking the weighted average of $\nabla_{t,x}$ and $\nabla_{t,y}$ over adjacent triangles $t\in\mathcal{N}(i)$, with weights given by the angle between the two sides of the triangle adjacent to the vertex. The resulting $\vec{\nabla}=(\nabla_x, \nabla_y)^T$ is a $2\times p\times p$ stack of matrices defined such that $\vec{\nabla}\mathbf{f}$ produces a $2\times p$ matrix representing the gradient of $f(x, y)$ at the mesh vertices, with the first and second rows of $\vec{\nabla}\mathbf{f}$ containing the $x$ and $y$ components of the gradient, respectively.}

\section{Spatially inhomogeneous $\lambda$}
\label{appendix:inhomogeneous}
\begin{color}{blue}
The London equation (Equation~\ref{eq:london}) is valid only under the assumption that the London penetration depth $\lambda$, a proxy for the superfluid density, is constant as a function of position~\cite{Tinkham2004-zn}. In cases where the superfluid density varies as a function of position, Ginzburg-Landau theory provides a more accurate description of the magnetic response of the system. Nevertheless, in an effort to model inhomogeneous superconductors using London theory, one can write out the ``inhomogeneous second London equation'' for a superconductor with spatially-varying London penetration depth $\lambda(\vec{r})$~\cite{Cave1986-js, Kogan2011-zn}:

\begin{align}
\begin{split}
    \label{eq:london_inhomogeneous_3d}
    \vec{H}(\vec{r})&=-\vec{\nabla}\times\left(\lambda^2(\vec{r})\vec{j}(\vec{r})\right)\\
    &=-\left(\lambda^2(\vec{r})\vec{\nabla}\times\vec{j}(\vec{r}) + \vec{\nabla}\lambda^2(\vec{r})\times\vec{j}(\vec{r})\right).
\end{split}
\end{align}

@@

Note that, unlike Equation~\ref{eq:london} in which $\Lambda$ is assumed to be constant as a function of position $\pvec{r}$, solutions to Equation~\ref{eq:london_inhomogeneous_2d} do not necessarily satisfy the fluxoid quantization condition $\Phi^f_S=0$ for simply-connected superconducting regions $S$ in which $\vec{\nabla}\Lambda(\pvec{r})\neq0$ , where
\begin{equation}
	\Phi^f_S=\underbrace{\int_S\mu_0H_z(\pvec{r})\,\mathrm{d}^2r}_{\text{``flux part''}} + \underbrace{\oint_S\mu_0\Lambda(\pvec{r})\vec{J}(\pvec{r})\cdot\mathrm{d}\pvec{r}}_{\text{``supercurrent part''}}.
\end{equation}
\end{color}
